---
title: "strptimer"
author: "Brandon Taylor"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{strptimer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Import the package. We will also make heavy usage of chaining: see magrittr's documentation.

```{r}
library(strptimer)
library(magrittr)
```

# Base Components
Let's see what kind of componenets we can use in our time format. 

```{r}
time_bases()
```

Each of these base time components can be used in a time format:

```{r}
time_format(year, month, day)
```

# Modifications
Each base component can be modified in special ways. Let's say we are curious about the time options for modifying month:

```{r}
"month" %>% base_options
```

The default value will have all always have all no options select. Each option has a corresponding function, which can assign that option. Each such function takes only one argument, except for digits (see example below).

```{r}
time_format(month %>% short %>% name)
```

For the most part, time options should be self explanatory. For more information, codes can be looked up in the `?strptime` documentation. Note that many time formats are possible to build but do not have corresponding codes.

```{r, error = TRUE}
time_format(month %>% short %>% roman)
```

# Example

Let's build a complicated date format just for fun:

```{r}
time_format(year %>% short %>% religious,
            "/",
            month %>% name %>% short,
            "/",
            day %>% roman,
            
            tab,
            
            hour %>% twelve %>% roman,
            ":",
            minute %>% roman,
            ":",
            second %>% digits(3),
            " ",
            am_pm,
            " ",
            timezone %>% name)
```
